Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-16 sanitation-psp14/tr/strings_chapter.tex
some TS work for lambda p and slight cleanup of current translation proof.

@@

\begin{thm}[Translation Correctness]\label{thm:trcorrect}
  If $\tctx \vdash e : \sigma$ then 
  there exists an $\iota$ such that $\trden{e} = \iota$
  and $\trden{\tctx} \vdash \iota : \trden{\sigma}$.
  Furthermore, $e \sreduces v$ and
  $\iota \treduces \dot{v}$ such that
  $\trden{v} = \dot{v}$.
\end{thm}
\begin{proof}
We present a proof by induction on the derivation that $\tctx \vdash e : \sigma$.
we write $e \leadsto \iota$ as shorthand for the final property.

@@

By definition of the translation ($\trden{\cdot}$) the following statements hold:
\begin{align}
\trden{\rstr{s}} &= \str{s} \\
\trden{\stringin{r}} &= \str \\
\trden{\emptyset} &= \emptyset
\end{align}
Note that $\emptyset \vdash \str{s} : \str$ by P-T-Str.
Recall that contexts are standard and, in particular, can be weakened.
So since $\trden{\tctx}$ is either a weakening of $\emptyset$ or $\emptyset$ itself,
$\trden{\tctx} \vdash \tstr{s} : \str$ by weakening.

Summarily, $\str{s}$ is a term of $\lambdap$ such that $\trden{\tctx} \vdash \str{s} : \trden{\sigma}$

>>>>

\item \textbf{Case SS-E-Replace-Left}.
Suppose that $e = \rreplace{r}{e_1}{e_2} \mapsto \rreplace{r}{e_1'}{e_2}$ when $e_1 \mapsto e_1'$.
The only rule that applies is S-T-Replace, so
$\emptyset \vdash e : \stringin{\lreplace{r}{r_1}{r_2}}$ where:
\begin{align*}
\emptyset &\vdash e_1 : \stringin{r_1} \\
\emptyset &\vdash e_2 : \stringin{r_2}
\end{align*}
By induction, $\emptyset \vdash e_1' : \stringin{r_1}$.
Therefore, $\emptyset \vdash \rreplace{r}{e_1'}{e_2} : \stringin{\lreplace{r}{r_1}{r_2}}$ by S-T-Replace.

\item \textbf{SS-E-Replace-Right}.
Suppose that $e = \rreplace{r}{e_1}{e_2} \mapsto \rreplace{r}{e_1'}{e_2}$ when $e_1 \mapsto e_1'$.
The only rule that applies is S-T-Replace, so
$\emptyset \vdash e : \stringin{\lreplace{r}{r_1}{r_2}}$ where:
\begin{align*}
\emptyset &\vdash e_1 : \stringin{r_1} \\
\emptyset &\vdash e_2 : \stringin{r_2}
\end{align*}
By induction, $\emptyset \vdash e_1' : \stringin{r_1}$.
Therefore, $\emptyset \vdash \rreplace{r}{r_1'}{r_2} : \stringin{\lreplace{r}{r_1}{r_2}}$ by S-T-Replace.

\item \textbf{SS-E-Replace}
Suppose that $e = \rreplace{r}{\rstr{s_1}}{\rstr{s_2}} \mapsto \rstr{\lsubst{r}{s_1}{s_2}}$ 
The only rule that applies is S-T-Replace, so
$\emptyset \vdash e : \stringin{\lreplace{r}{r_1}{r_2}}$ where:
\begin{align*}
\emptyset &\vdash \rstr{s_1} : \stringin{r_1} \\
\emptyset &\vdash \rstr{s_2} : \stringin{r_2}
\end{align*}

Therefore, it suffices to show that $\emptyset \vdash \rstr{\lsubst{r}{s_1}{s_2}} : \stringin{\lreplace{r}{r_1}{r_2}}$
or, equivalently, that $\lsubst{r}{s_1}{s_2} \in \lang{\lreplace{r}{r_1}{r_2}}$.
This follows from the fact that $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$.
The only rule that applies is S-T-Replace, so
$\emptyset \vdash e : \stringin{\lreplace{r}{r_1}{r_2}}$ where:
\begin{align*}
\emptyset &\vdash \rstr{s_1} : \stringin{r_1} \\
\emptyset &\vdash e_2 : \stringin{r_2}
\end{align*}
By induction, $\emptyset \vdash e_2' : \stringin{r_2}$.
Therefore, $\emptyset \vdash \rreplace{r}{\rstr{s_1}}{e_2'} : \stringin{\lreplace{r}{r_1}{r_2}}$ by S-T-Replace.

% bookmark-nrf
\item

@@

\begin{thm}[Translation Correctness]\label{thm:trcorrect}
  If $\tctx \vdash e : \sigma$ then 
  there exists an $\iota$ such that $\trden{e} = \iota$
  and $\trden{\tctx} \vdash \iota : \trden{\sigma}$.
  Furthermore, if $e \sreduces v$ then
  $\iota \treduces \dot{v}$ such that
  $\trden{v} = \dot{v}$.
\end{thm}
\begin{proof}
We present a proof by induction on the structure of $e$ \todo{why not on the typing derivation?}.
We write $e \leadsto \iota$ as shorthand for the final property.

@@

By definition of the translation ($\trden{\cdot}$) the following statements hold:
\begin{align}
\trden{\rstr{s}} &= \tstr{s} \\
\trden{\stringin{r}} &= \str \\
\trden{\emptyset} &= \emptyset
\end{align}
Note that $\emptyset \vdash \tstr{s} : \str$ by P-T-Str.
Recall that contexts are standard and, in particular, can be weakened.
So since $\trden{\tctx}$ is either a weakening of $\emptyset$ or $\emptyset$ itself,
$\trden{\tctx} \vdash \tstr{s} : \str$ by weakening.

Summarily, $\tstr{s}$ is a term of $\lambdap$ such that $\trden{\tctx} \vdash \tstr{s} : \trden{\sigma}$
